Classical Planning with Simulations: \\ Results on the Atari Video Games

### 2015-02-05 ijcai15-paper/paper.tex
Macro for MCTS

\newcommand{\propername}[1]{\textsc{#1}}
\newcommand{\eqdef}{\stackrel{\hbox{\tiny{def}}}{=}}
%\newcommand{\IW}{{\textit{IW}}}
%\newcommand{\SIW}{{\textit{SIW}}}
%\newcommand{\ID}{{\textit{ID}}}
%\newcommand{\BRFS}{{\textit{BrFS}}}
%\newcommand{\BFS}{{\textit{\BFS}}}
%\newcommand{\UCT}{{\textit{UCT}}}
\newcommand{\IW}{{\textsc{IW}}}
\newcommand{\SIW}{{\textsct{SIW}}}
\newcommand{\ID}{{\textsc{ID}}}
\newcommand{\BRFS}{{\textsc{BrFS}}}
\newcommand{\BFS}{{\textsc{2BFS}}}
\newcommand{\UCT}{{\textsc{UCT}}}

@@

We have shown experimentally that width-based algorithms like $\IW(1)$ and \BFS\
that originate in work in classical planning,  can be used to play  the Atari video
games where they  achieve  state-of-the-art performance. The  results also  suggest 
more generally the potential of width-based methods for planning with simulators when factored, 
compact action models are not available. In this sense, the scope of these planning methods 
is broader than those of heuristic-search planning methods that require propositional
encodings of actions and goals, and with suitable extensions, 
may potentially  approach the scope of MCTS-methods like UCT that work on simulators as well.

>>>>

\newcommand{\propername}[1]{\textsc{#1}}
\newcommand{\eqdef}{\stackrel{\hbox{\tiny{def}}}{=}}
%\newcommand{\IW}{{\textit{IW}}}
%\newcommand{\SIW}{{\textit{SIW}}}
%\newcommand{\ID}{{\textit{ID}}}
%\newcommand{\BRFS}{{\textit{BrFS}}}
%\newcommand{\BFS}{{\textit{\BFS}}}
%\newcommand{\UCT}{{\textit{UCT}}}
\newcommand{\IW}{{\textsc{IW}}}
\newcommand{\SIW}{{\textsct{SIW}}}
\newcommand{\ID}{{\textsc{ID}}}
\newcommand{\BRFS}{{\textsc{BrFS}}}
\newcommand{\BFS}{{\textsc{2BFS}}}
\newcommand{\UCT}{{\textsc{UCT}}}
\newcommand{\MCTS}{{\textsc{MCTS}}}

@@

We have shown experimentally that width-based algorithms like $\IW(1)$ and \BFS\
that originate in work in classical planning,  can be used to play  the Atari video
games where they  achieve  state-of-the-art performance. The  results also  suggest 
more generally the potential of width-based methods for planning with simulators when factored, 
compact action models are not available. In this sense, the scope of these planning methods 
is broader than those of heuristic-search planning methods that require propositional
encodings of actions and goals, and with suitable extensions, 
may potentially  approach the scope of \MCTS\ methods like \UCT\ that work on simulators as well.
